### 2023-09-25 appendices/paper_brief.tex
Work on background and main contributions

\paragraph{Moving forward} 
Most of the seminal work has focused on improving speech recognition \cite{schneider_wav2vec_2019, baevski_wav2vec_2020}. This focus has gained traction over the last couple of years, as computational resources have become more accessible and end-to-end models \cite{graves_connectionist_2006, chan_listen_2015} have been established as the dominant approach to speech recognition \cite{gulati_conformer_2020}. It is important to stress that self-supervised models, such as wav2vec 2.0 \cite{baevski_wav2vec_2020}, represent a breakthrough, and recent successful approaches build upon this method. That is, deep self-attention models combined with masking \cite{hsu_hubert_2021, wang_unispeech_2021, chen_wavlm_2021}. This development mirrors years of rapid progress in masked language modeling within natural language processing \cite{devlin_bert_2018,clark_2020_electra} and we expect this to continue for unsupervised neural speech representation learning.

>>>>

\paragraph{Moving forward} 
Most of the seminal work has focused on improving speech recognition \cite{schneider_wav2vec_2019, baevski_wav2vec_2020}. This focus has gained traction over the last couple of years, as computational resources have become more accessible and end-to-end models \cite{graves_connectionist_2006, chan_listen_2015} have been established as the dominant approach to speech recognition \cite{gulati_conformer_2020}. It is important to stress that self-supervised models, such as wav2vec 2.0 \cite{baevski_wav2vec_2020}, represent a breakthrough, and recent successful approaches build upon this method. That is, deep self-attention models combined with masking \cite{hsu_hubert_2021, wang_unispeech_2021, chen_wavlm_2021}. This development mirrors years of rapid progress in masked language modeling within natural language processing \cite{devlin_bert_2018,clark_electra_2020} and we expect this to continue for unsupervised neural speech representation learning.

### 2023-09-25 appendices/supplementary_modelagnostic.tex
Some formatting and changes to labels
Work on background and main contributions

\chapter[supplementary material: model-agnostic out-of-distribution detection using combined statistical tests]{Supplementary material: Model-Agnostic Out-of-Distribution Detection Using Combined Statistical Tests}
\label{app:modelagnostic}
\ifthenelse{\equal{\skipappendices}{true}}{}{

@@

\section{Comparison with the original DoSE statistics}
As the last experiment, we study how our proposed method with our model agnostic statistic performs against DoSE using the original statistics proposed in \cite{morningstar_density_2021}. For the VAEs model, they suggested to use the following 5 statistics: the posterior/prior cross-entropy $\text{H}[q_{\phi}( \textbf{z}\mid \textbf{x}), p(\textbf{z})]$, the posterior entropy $\text{H}[q_{\phi}(\textbf{z}\mid \textbf{x})]$, the posterior/prior KL divergence $\text{D}_{\text{KL}}[q_{\phi}(\textbf{z}\mid \textbf{x}) \mid \mid p(\textbf{z})]$, the posterior expected log-likelihood $\mathbb{E}_{q_{\phi}(\textbf{z}\mid \textbf{x})}[\log q_{\phi}(\textbf{z}\mid \mathbf{x})]$, and the log-likelihood $\log \mathbb{E}_{q_{\phi}(\textbf{z}\mid \textbf{x})} \left[ \frac{p_{\theta}(\textbf{x}, \textbf{z})}{q_{\phi}(\textbf{z}\mid \textbf{x})}\right]$. For DoSE on Glow, instead, they considered three metrics: the log-likelihood $p_{X}(\textbf{x}\mid \theta_n)$ and its two components, i.e.\@ the log-probability of the latent variable $p_{Z}(\textbf{z}\mid \textbf{x}, \theta_n)$ and the log-determinant of the Jacobian $\log | \text{J}_{f}(\textbf{x})|$.

>>>>

\chapter[supplementary material: model-agnostic out-of-distribution detection using combined statistical tests]{Supplementary material: Model-Agnostic Out-of-Distribution Detection Using Combined Statistical Tests}
\label{app:supplementary-modelagnostic}
\ifthenelse{\equal{\skipappendices}{true}}{}{

@@

\section{Comparison with the original DoSE statistics}
As the last experiment, we study how our proposed method with our model agnostic statistic performs against DoSE using the original statistics proposed in \cite{morningstar_density_2021}. For the VAEs model, they suggested to use the following 5 statistics: the posterior/prior cross-entropy $\text{H}[q_{\phi}( \textbf{z}\mid \textbf{x}), p(\textbf{z})]$, the posterior entropy $\text{H}[q_{\phi}(\textbf{z}\mid \textbf{x})]$, the posterior/prior KL-divergence $\text{D}_{\text{KL}}[q_{\phi}(\textbf{z}\mid \textbf{x}) \mid \mid p(\textbf{z})]$, the posterior expected log-likelihood $\mathbb{E}_{q_{\phi}(\textbf{z}\mid \textbf{x})}[\log q_{\phi}(\textbf{z}\mid \mathbf{x})]$, and the log-likelihood $\log \mathbb{E}_{q_{\phi}(\textbf{z}\mid \textbf{x})} \left[ \frac{p_{\theta}(\textbf{x}, \textbf{z})}{q_{\phi}(\textbf{z}\mid \textbf{x})}\right]$. For DoSE on Glow, instead, they considered three metrics: the log-likelihood $p_{X}(\textbf{x}\mid \theta_n)$ and its two components, i.e.\@ the log-probability of the latent variable $p_{Z}(\textbf{z}\mid \textbf{x}, \theta_n)$ and the log-determinant of the Jacobian $\log | \text{J}_{f}(\textbf{x})|$.
